Toronto Beach Data

### 2024-09-26 paper/paper.qmd
Appendix Completed

---
title: "Data Analysis of the Relationship Between Date, Air Temperature, Whether It Rains or Not, Water Temperature, and Observations of Water Fowls at Beaches in Toronto"
author: "Yanzun Jiang"
date: today
date-format: long
thanks: "Code and data supporting this analysis is available at: https://github.com/Stary54264/Toronto-Beach-Data"
abstract: "This paper conducted a basic data analysis on data of beaches in Toronto. The variables mentioned in the tile are highly correlated. The analysis can help us to know better about beaches in Toronto. Further, it helps meteorologists to monitor climate changes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@sec-data

&nbsp; @sec-data-1

&nbsp; @sec-data-2

&nbsp; &nbsp; @sec-data-2-1

&nbsp; &nbsp; @sec-data-2-2

&nbsp; &nbsp; @sec-data-2-3

&nbsp; &nbsp; @sec-data-2-4

@sec-results

@sec-discussion

@@

```{r}
#| label: tbl-data
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-air-temp
#| fig-cap: Histogram of Air Temperature
#| echo: false
#| warning: false
#| message: false

@@

# Appendix {-}

# Additional data details

>>>>

---
title: "Toronto Beach Data"
subtitle: "Data Analysis of the Relationship Between Date, Air Temperature, Whether It Rains or Not, Water Temperature, and Observations of Water Fowls"
author: "Yanzun Jiang"
date: today
date-format: long
thanks: "Code and data supporting this analysis is available at: https://github.com/Stary54264/Toronto-Beach-Data"
abstract: "This paper conducted a basic data analysis on data of beaches in Toronto. The variables mentioned in the tile are highly correlated. The analysis can help us to know better about beaches in Toronto. Further, it helps meteorologists to monitor climate changes."
format: pdf
number-sections: true
bibliography: references.bib
---

@@

@sec-data
@sec-data-1
@sec-data-2
@sec-data-2-1
@sec-data-2-2
@sec-data-2-3
@sec-data-2-4
@sec-results
@sec-discussion

@@

```{r}
#| label: tbl-data
#| tbl-cap: Preview of Data
#| echo: false
#| warning: false
#| message: false

@@

```{r}
#| label: fig-air-temp
#| fig-cap: Air Temperature at Toronto Beaches from
#| echo: false
#| warning: false
#| message: false

@@

# Appendix {#sec-appendix}

## Dataset and Graph Sketches {#sec-appendix-1}

Sketches depicting both the desired dataset and the graphs generated in this analysis are available in the GitHub Repository.

## Data Cleaning {#sec-appendix-2}

The data cleaning process involved renaming variables, filtering out useless columns from the raw dataset, filtering out observations with NAs, and removing the outliers using z-scores.
